Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2015-05-15 tex/scam/additive_faithful.tex
a

\begin{definition}
\label{defn:boundary-point}
Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$. We say that
$p(\mathbf{x})$ satisfies the \emph{boundary flatness condition} if
for all $j$, for all $\mathbf{x}_{-j}$, and for all $x_j \in [0,
  \epsilon) \cup (1-\epsilon, 1]$ for some arbitrarily small $\epsilon
> 0$, 
\begin{enumerate}[(i)]
\item $p(\mathbf{x}_{-j} \given x_j)$ is twice differentiable in
$x_j$,
\item $p(\mathbf{x}_{-j} \given x_j), \frac{\partial
  p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}, \frac{\partial^2
  p(\mathbf{x}_{-j} \given x_j) }{\partial^2 x_j}$ are bounded,
\item for $x_j=0$ and $x_j=1$,
\begin{equation}
\frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}  =  
\frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0.
\end{equation}
\end{enumerate}

>>>>

\begin{definition}
\label{defn:boundary-point}
Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$. We say that
$p(\mathbf{x})$ satisfies the \emph{boundary flatness condition} if
for all $j$ and for all $\mathbf{x}_{-j}$, 
\begin{enumerate}[(i)]
\item the derivatives $\frac{\partial
  p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}, \frac{\partial^2
  p(\mathbf{x}_{-j} \given x_j) }{\partial^2 x_j}$ exist and are bounded,
for all $x_j \in [0,  \epsilon) \cup (1-\epsilon, 1]$ 
with $\epsilon > 0$ arbitrarily small,
\item for $x_j=0$ and $x_j=1$,
$\frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}  =  
\frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0$.
\end{enumerate}
